\documentclass[11pt]{article}

\usepackage{fullpage}
\usepackage[pdftex]{graphicx}
\usepackage{setspace}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{hyperref}
\usepackage{bookmark}
\renewcommand{\thesection}{}
\renewcommand{\thesubsection}{\arabic{subsection}}
\makeatletter
\def\@seccntformat#1{\csname #1ignore\expandafter\endcsname\csname the#1\endcsname\quad}
\let\sectionignore\@gobbletwo
\let\latex@numberline\numberline
\def\numberline#1{\if\relax#1\relax\else\latex@numberline{#1}\fi}
\makeatother
\begin{document}


\section{\#offtopia law guide}

This document is merely a summary of the most important laws helpful for everyday
activity.


\subsection{Terminology}

\begin{itemize}
\item \texttt{law}: A passed proposal. A proposal requires three contiguous votes
by unique non-bot members of the channel to be passed.

Laws need not effect active behavior on the channel, and can be passed because of
Rule of Funny.

\item \texttt{malcompliance}: The act of complying in the worst possible manner. Or,
as the Finnish define it, ``following the letter of the law while pissing on the spirit''.

Examples:
\begin{quote}
``Hey could you test sortix?'' ``test -f sortix.iso \# Yep. It's a file.'' \\
``Hey, can you give me some water?'' ``You mean aqua?'' ``...sure.'' *gives aqua fortis*
\end{quote}

\item \texttt{filibuster}: Anything that is sent on the channel, and can stop a
law from being passed, is known as a filibuster. This is line in with the literal meaning,
``obstructs progress in a legislative assembly''.

\item \texttt{proposal}: Anything that can filibuster can be a proposal.

\item \texttt{new ancient law}: A law that has always been true, 
but was only recently discovered and legislated.

\item \texttt{lawrememberer}: The person responsible for maintaining the lawlist,
currently `nortti'.

\item \texttt{lawspeaker}: The person who interprets and clarifies the law,
currently `nortti'.

\item \texttt{triminority}: The three required to pass a law. Can be used to refer to
an actual group, or a hypothetical group.

\item \texttt{triumvirate}: People who are more active with channel work, and have
additional rights with ChanServ. Currently consists of `FireFly', `heddwch', `meowrobot',
`nortti', `puckipedia', `shikhin', `sortie', `vehk', and `ybden'.

\item \texttt{vote}: Anything described under `Voting.Syntaxen'.
\end{itemize}


\subsection{Behaving}

\begin{itemize}
\item \url{https://gitlab.com/sortie/mmmm/blob/master/mmmm.txt} (MMMM).
A collection of rules and guidelines that evolved from horrors that won't be mentioned
here; currently in helpful form. By new ancient law, MMMM is lawful.

\item Calling women subhuman; making racist, homophobic, or transphobic
comments; calling people with disabilities leeches and subhuman;
telling people with mental illnesses to kill themselves; or other comparable acts
are to be prohibited, except in cases of clear sarcasm.

\item If someone lays out a boundary to you, you are to respect it. No "jokes" where you
repeatedly violate it after being specifically told so. If you violate a boundary by accident,
apologise.

\item Mark NSFW content. Linked NSFW content should be marked, preferably with
\texttt{NSFW} or \texttt{[NSFW]}.

\item Avoid funkicking.
`Funkicking' is where you kick someone just for fun, or for some insignificant reason.
Exception to this is if the person you're `funkicking' does not mind the fun kick.

\item Do not kick idlers, unless for abuse or clear violations of channel law.

Idlers are defined as people whose last activity has been 5 minutes ago (where activity
implies messages or nick changes as a response to something in the channel), or who
have marked themselves away (e.g. by \texttt{bbl}).
\end{itemize}


\subsection{Logs}

\begin{itemize}
\item There is a public log that logs the last hundred lines of the channel, except those that
begin with \texttt{nolog:} or \texttt{[nolog]}.
\item Publishing channel logs otherwise without explicit agreement from the channel is
prohibited.
\item The gopher server serving the public logs is allowed to collect IPs, requested paths,
and user agents of connecting users; these are not retained for over a month except in cases
of abuse.
\end{itemize}


\subsection{Voting}


\subsubsection{Basics}

At every moment, there is an active proposal and a vote count.

If a vote that doesn't refer to the current active proposal is cast, the active proposal
changes to the new proposal, and the vote count resets to 0. A filibuster sets the active
proposal to itself and resets the vote count to 0.

A vote increments the vote count by 1 after change of proposal (if required).

When the vote count reaches 3, the active proposal becomes a law.


\subsubsection{Syntaxen}
There are several different kinds of syntaxes for voting on laws. They're all based
on the original syntax of \texttt{:D}, with various modifications.

\begin{itemize}
\item \texttt{:D}

The most basic form. Votes for the current active proposal.

\item \texttt{:D\~{}N}

Votes N proposals back. Is 0-indexed, so \texttt{:D\~{}0} is equivalent to \texttt{:D}.

\item \texttt{:D\^{} :D\^{}\^{} :D\^{}\^{}\^{} ...}

Equivalent to \texttt{:D\~{}N}, where N is the number of `\^{}'s.

\item \texttt{:D\~{}kick}

Refers to last kick. Can only be used right after a kick, or a kick followed by a join
by the kicked person.

\item \texttt{nick: :D, nick: :D\~{}N, nick: :D\^{}}

Same as without the \texttt{nick: } prefix, but instead refer to the relevant proposal
made by `nick'. \texttt{nick, } can be used instead of \texttt{nick: }.
\end{itemize}


\subsubsection{What counts as a filibuster/proposal?}

\begin{itemize}
\item Filibustering messages \emph{are} proposals, \emph{unless} they're sent by 
bots to explain something in the previous message (e.g. title bot, automatic translation) 
\emph{or} they begin with \texttt{nolog:} or \texttt{[nolog]}.
\item Bot messages sent as a response to direct command (e.g. program evaluation,
non-automatic translation) \emph{are} proposals.
\item Bot messages that are generally to be ignored in the legislative process (e.g. title
bot, automatic translation) \emph{are} proposals \emph{if} intended to disrupt.
\item Notices are treated like messages (except they can't be used to vote).
\item Nick changes \emph{are not} proposals, \emph{unless} they are a direct response
to something in channel \emph{or} are disruptive.
\item Kicks and mode changes \emph{are} proposals.
\item Joins \emph{are not} proposals, \emph{unless} it is a first join \emph{or} intended
to disrupt.
\item Parts and quits \emph{are not} proposals, \emph{unless} intended to disrupt.
\item Special behaviour: valid votes with \texttt{:D:} or \texttt{D:} substituted for \texttt{:D}
can \emph{not} act as proposals. These messages still filibuster.
\end{itemize}


\subsection{Additional stuff}

\begin{itemize}
\item In cases where there is disagreement on whether something passed, the
lawrememberer's point of view is used.
\item The person who opens the vote on a proposal must provide the law to lawrememberer,
if requested to do so.
\item Zero-width spaces in votes are to be ignored.
\item It is a good custom to vote on one's own proposal last.
\end{itemize}

\end{document}
